Article results

### 2022-07-16 analysis/article-results.Rmd
Removed logreg recal/started cleaning

# Load libraries for knitting
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)

# Source functions
source("data-raw/prepare_raw_data.R")
source("R/imputation-helpers.R")
source("R/model-validation-helpers.R")
source("R/calplot-MI.R")

@@

# Set global setting
theme_set(theme_minimal(base_size = 14))
```

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin
  )
)

@@

For continous variables:

@@

# Check proportion of complete cases in target analysis (quite good, compare results)
mean(complete.cases(dat_develop[, c("Mc_FailedFemoralApproach", candidate_predictors)]))
mean(complete.cases(dat_valid[, c("Mc_FailedFemoralApproach", candidate_predictors)]))
mean(complete.cases(dat_to_impute[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

@@

## Model update 1: logistic recalibration

```{r log-recal}
# 
imps_valid$lp_valid <- lp_valid
mod_recal <- glm(
  Mc_FailedFemoralApproach ~ lp_valid, 
  family = binomial(), 
  data = imps_valid
)
boots_valid <- group_resample(imps_valid, id_var = ".id", 
                              B = 50, 
    boot_id_name = ".id_boot")

boots_cals <- map_dfr(boots_valid, function(boot_dat) {
  mod_recal_boot <- glm(
  Mc_FailedFemoralApproach ~ lp_valid, 
  family = binomial(), 
  data = boot_dat
)
  calibration_intercept_slope(
    imps_valid$Mc_FailedFemoralApproach, predict(mod_recal_boot, newdata = imps_valid)
  )
})
colMeans(boots_cals)

# Calib plot
library(splines)
ggplot() +
  geom_smooth(
    data = cbind.data.frame(
      "predicted" = predict(mod_recal, type = "response"), #wrrooong
      "outcome" = as.numeric(imps_valid$Mc_FailedFemoralApproach) - 1L,
      "imp" = imps_valid$.imp
    ),
    aes(
      x = predicted,
      y = outcome,
      group = imp
    ), method = "glm",
    formula = y ~ ns(x, 5),
    method.args = list(family = "binomial"),
    se = FALSE,
    col = "gray",
    alpha = 0.7
  ) +
  geom_abline(intercept = 0, slope = 1) +
  lims(x = c(0, 1), y = c(0, 1))
```

## Model update 2: combined cohort re-estimation

@@

```{r interaction-by-cohort}
split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |>  
  ggforestplot::forestplot(
    name = term,
    estimate = estimate,
    se = std.error
  )

@@

```{r combined-validation}
imps_combined <- imps_all %>% 
  filter(imps_label == "imps_combined")

mod_combined <- validation_comb_lambdamin$model_fit
validation_comb_lambdamin$model_fit$lambda
mod_combined$beta

@@

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.55),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()

# Try simpler version of cal plot
lp_combined <- predict(
  validation_comb_lambdamin$model_fit,
  newx = subset(
    x = model.matrix(model_formula, data = imps_combined), 
    select = -`(Intercept)`
  )
)

df <- cbind.data.frame(
      "predicted" = drop(lp_combined),
      "outcome" = as.numeric(imps_combined$Mc_FailedFemoralApproach) - 1L,
      "imp" = imps_combined$.imp
    )

binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}

ggplot(data = df, aes(plogis(predicted), outcome)) +
  binomial_smooth(
    aes(x = predicted),
    formula = y ~ splines::ns(x, 3),
    se = FALSE
  ) #+
  scale_x_continuous(trans = "log", limits = c(0.1, 1))
  geom_smooth(
    ,
    aes(
      x = predicted,
      y = outcome#,
      #group = imp
    ), 
    method = "glm",
    #formula = y ~ splines::ns(x, 3),
    method.args = list(family = "binomial"),
    se = FALSE,
    col = "gray",
    alpha = 0.7
  ) +
  geom_abline(intercept = 0, slope = 1) +
  lims(x = c(0, 1), y = c(0, 1))

```

>>>>

# Load libraries for knitting
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
```

```{r objs}
# Source functions
source("data-raw/prepare_raw_data.R")
source("R/imputation-helpers.R")
source("R/model-validation-helpers.R")
source("R/calplot-MI.R")

@@

# Set global setting
theme_set(theme_minimal(base_size = 14))

tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin
  )
)

@@

For continuous variables:

@@

# Check proportion of complete cases in target analysis (quite good, compare results)

# Development
mean(complete.cases(dat_develop[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Validation
mean(complete.cases(dat_valid[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

# Combined
mean(complete.cases(dat_to_impute[, c("Mc_FailedFemoralApproach", candidate_predictors)]))

@@

## Model update: combined cohort re-estimation

@@

```{r interaction-by-cohort}
imps_combined <- imps_all %>% 
  filter(imps_label == "imps_combined")

split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |>  
  ggforestplot::forestplot(
    name = term,
    estimate = estimate,
    se = std.error
  )

@@

```{r combined-validation}
mod_combined <- validation_comb_lambdamin$model_fit
#validation_comb_lambdamin$model_fit$lambda

mod_coefs_comb <- as.matrix(coef(mod_combined))
colnames(mod_coefs_comb) <- "Coefficients"

# Print penalied model coefficients
knitr::kable(data.frame(mod_coefs_comb))

@@

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.55),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()
```
